Perception of Work Demands and Resources: Does Volume Relate to Engagement, Stress, or Burnout?

### 2022-09-23 SIOP2023/Counts/Submission_ResourceCount.Rmd
Draft discussion added

  Our fourth prediction suggested a positive association between total resources and total challenge demands. Here, we observed a strong positive relationship, so much so that it could be argued that these two variables are capturing the same thing (r = .86), as fully 74% of the variability was shared. 
  To illustrate this relationship further, we computed a percentage of matches within person for the subset of job characteristics respondents agreed were a part of their jobs (excluding those characteristics rated as not part of one's job). Figure ?? shows the distribution of the proportion of matches by person.

@@

>>>>

  Our fourth prediction suggested a positive association between total resources and total challenge demands. Here, we observed a strong positive relationship, so much so that it could be argued that these two variables are capturing the same thing (r = .86), as fully 74% of the variability was shared.

  To illustrate this relationship further, we computed a percentage of matches within person for the subset of job characteristics respondents agreed were a part of their jobs (excluding those characteristics rated as not part of one's job). Figure ?? shows the distribution of the proportion of matches by person.

@@

*Discussion*

The major goal of this paper was to further explore the relationships among total perceived challenge demands, hindrance demands, and resources and outcomes of engagement, stress, and burnout. Additionally, we considered whether resources and challenge demands were perceived as distinct, and finally, whether the patterns were similar across job categories/types of work. The results suggest a positive relationship between both resources and engagement (H1a), and challenge demands and engagement (H2a). Employers would benefit from understanding that at leas the perception of having “more” resources and more challenge demands in a job is highly associated with reported engagement. While not a causal relationship, it points to the potential value of these kinds of employee support nonetheless. The other relationships with outcomes of stress and burnout were not supported, suggesting that the sheer number of resources, challenges, and hindrances are not significantly related to these negative outcomes. It is possible that rather than volume, categorically some demands are more related to these outcomes than others.
 Further, total resources were highly associated challenge demands (supporting H4). We could even argue, given the magnitude of the correlation, that they are capturing the same thing (74% overlap with a correlation of .86). Need to also talk about our exploratory findings regarding patterns across job type
Limitations and Future Directions
As with any piece of research, the process and results have limitations, but also provide a variety of additional directions to pursue in the future. First, while a strength of this project, arguably, is the use of O*Net items, practical considerations limited the number of job characteristics we could include in our survey. Future study could consider additional or other O*Net items. We conceptualized resources and demands in terms of perceived total amounts. It may be the case that certain kinds of resources or challenges are more strongly associated with engagement than others, and such, future research could explore the importance of resources/challenges categorically. Further, our study was limited to three outcomes of interest. It would be especially interesting to explore additional outcomes (e.g., job satisfaction) as well, or whether volume of resources and demands operationalized in this way are related to other behaviors (e.g., turnover intention, perceived organizational support, commitment).
